Dear AC,

many thanks for coordinating the review of this work.
We would like to raise a special concern about the fairness and credibility of the comment from the reviewer xgZ6. 
Please find below a list of issues raising our concern:

1. 

Although the reviewer xgZ6 claimed xgZ6 is absolutely certain about the evaluation the evaluation  

We are honored to receive valuable feedback from the reviewers and thank you for your assignment. The only concern we have some opinions about is the last reviewer, , who did not understand the paper. 

Almost all the weaknesses xgZ6 mentioned were that he couldn't understand the method. For example, he even couldn't figure out the most basic thing in the field of Adversarial Robustness that the prompt for inference and the prompt for attack are independent to each other. On the other hand, the other two reviewers did not raise any questions about not understanding the method. However, the confidence level the last reviewer xgZ6 gave was five, the highest level, and he thought he understood this method very well.

In conclusion, the reviewer xgZ6 raised the weaknesses which were all about the method understanding and did not understand our method. And the reviewer xgZ6 was very confident while other reviewers can easily understand our method. His evaluation would unfairly judge our paper. 

Kind regards,

Authors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To whom it may concern,

We appreciate the insightful feedback provided by the reviewers and express our gratitude for your assessment of our paper. We would like to address a specific concern regarding the comments from the last reviewer, xgZ6.

Our main issue revolves around the fact that Reviewer xgZ6 appears to have difficulty understanding the method in our paper. Many of the weaknesses highlighted by xgZ6 revolve around a misunderstanding of fundamental concepts, such as the independence between the prompt for inference and the prompt for attack in the field of Adversarial Robustness. Remarkably, the other two reviewers did not express any ambiguity regarding the comprehension of our method. It is noteworthy that despite struggling to understand the basics of our approach, Reviewer xgZ6 assigned the highest confidence level, five, which indicates a misunderstanding of our work.

In conclusion, the weaknesses identified by Reviewer xgZ6 pertain solely to a misunderstanding of our method. Given that the other reviewers, who easily comprehended our approach, did not raise similar concerns, we believe that Reviewer xgZ6's evaluation may unfairly impact the overall judgment of our paper.

We kindly request that the committee takes into consideration the discrepancy in understanding and confidence levels among the reviewers in their final assessment of our submission.

Thank you for your time and consideration.

Kind regards,

Authors
